Faithful Variable Screening for\\ High-Dimensional Convex Regression

### 2014-11-02 tex/scam/appendix.tex
edited through 8.2

We restate Theorem~\ref{thm:deterministic} first for convenience.

\begin{theorem} 
The following holds regardless of whether we impose the Lipschitz condition in optimization~\ref{opt:alternate_opt} and optimization~\ref{opt:alternate_opt_concave}.

Let $\{\hat{d}_k \}_{k \in S}$ be a minimizer of the restricted regression, that is, the solution to optimization (\ref{opt:alternate_opt}) where we restrict $k \in S$. 
Let $\hat{r} \coloneqq Y - \sum_{k \in S} \bar{\Delta}_k \hat{d}_k$ be the restricted regression residual. \\

Suppose for all $k\in S^c$, for all $i=1,...,n$, $\lambda_n > | \frac{1}{2n}
\hat{r}^\tran \mathbf{1}_{(i:n)}|$ where $\mathbf{1}_{(i:n)}$ is 1 on the coordinates of the $i$-th largest to the $n$-th largest entries of $X_k$ and 0 elsewhere.\\

Then the following are true:
\begin{enumerate}
\item Let $\hat{d}_k = 0$ for $k \in S^c$, then \{$\hat{d}_k\}_{k=1,...,p}$ is an optimal solution to optimization~\ref{opt:alternate_opt}. Furthermore, any solution to the optimization program \ref{opt:alternate_opt} must be zero on $S^c$.
\item For all $k \in S^c$, the solution to optimization~\ref{opt:alternate_opt_concave} must be 0 and must be unique.
\end{enumerate}
\end{theorem}

\begin{proof} 
We will omit the Lipschitz constraint in our proof here. It is easy to add that in and check that the result of the theorem still holds.\\

We first consider the first item in the conclusion of the theorem.

We will show that with $\{\hat{d}_k\}_{k=1,..,p}$ as constructed, we can set the dual variables to satisfy complementary slackness and stationary conditions: $\nabla_{d_k} \mathcal{L}(\hat{d})  = 0$ for all $k$.\\

@@

We now verify that stationarity holds also for $k \in S^c$. We fix one dimension $k \in S^c$ and let $\hat{r} = Y - \sum_{k' \in S} \bar{\Delta}_{k'} \hat{d}_{k'}$.

The Lagrangian form of the optimization, in terms of just $d_k$, is
\[
\mathcal{L}(d_k, \nu_k) =
  \frac{1}{2n} \big\| Y - \sum_{k' \in S} \bar{\Delta}_{k'} d_{k'} 
  -  \bar{\Delta}_k d_k \big\|_2^2 
   + \lambda \| \bar{\Delta}_k d_k\|_\infty
  - \sum_{i=2}^{n-1} \nu_{ki} d_{ki}
\]
with the constraint that $v_i \geq 0$ for all $i$.

The derivative of the Lagrangian is:
\begin{align*}
\partial_{d_k} \mathcal{L}(d_k) =  -\frac{1}{n} \bar{\Delta}_k^\tran ( Y - \sum_{k'\in S} \bar{\Delta}_{k'} d_{k'}  - \bar{\Delta}_k d_k )
        + \lambda \bar{\Delta}_k^\tran \mathbf{u}
      - \nu_k
\end{align*}
where $\mathbf{u}$ is the subgradient of $\| \bar{\Delta}_k d_k \|_\infty$, an $n$-vector such that $\| \mathbf{u}_T \|_1 = 1$ where $T = \{ i \,:\,  (\bar{\Delta}_k d_k)_i = \| \bar{\Delta}_k d_k \|_\infty \}$.

We now substitute in $d_{k'} = \hat{d}_{k'}$ for $k' \in S$, $d_k = 0$ for $k \in S$, and $r = \hat{r}$ and show that the duals can be set in a way to ensure that the derivatives are equal to 0.

\begin{align*}
\partial_{d_k} \mathcal{L}(\hat{d}_k) = -\frac{1}{n} \bar{\Delta}_k^\tran\hat{r} + \lambda \bar{\Delta}_k^\tran \mathbf{u}
           - \nu_k = 0 
\end{align*}
where $\| \mathbf{u} \| \leq 1$ and $\nu_k \geq 0$. It clear that to show stationarity, we only need to show that $-\frac{1}{n} \bar{\Delta}_k^\tran \hat{r} + \lambda \bar{\Delta}_k^\tran \mathbf{u} \geq 0$ hwere the inequality is element-wise.

Let us reorder the samples so that the $i$-th sample is the $i$-smallest sample. \\

We will construct $\gamma = 0$, and $\mathbf{u} = (-a, 0, ..., a)$ for some $0 < a < 1/2$. (coordinates of $\mathbf{u}$ correspond to the new sample ordering) We then just need to show that
\begin{align*}
- \frac{1}{n} \bar{\Delta}_k^\tran \hat{r} + \lambda \bar{\Delta}_k^\tran \mathbf{u} &\geq 0 \quad \Leftrightarrow \\
- \frac{1}{n} \Delta_k^\tran \hat{r} + \lambda \Delta_k^\tran \mathbf{u} &\geq 0 \quad \Leftrightarrow\\
- \frac{1}{n} \sum_{i > j} (X_{ki} - X_{kj}) \hat{r}_i + \lambda (X_{kn} - X_{kj})a &\geq 0 \quad 
   \textrm{for each } j \\
- \frac{1}{n} \sum_{i > j} \sum_{j < i' \leq i} \mathsf{gap}_{i'} \hat{r}_i 
    + \lambda (X_{kn} - X_{kj})a &\geq 0 \\
- \frac{1}{n} \sum_{i' > j} \mathsf{gap}_{i'} \sum_{i \geq i'} \hat{r}_i 
    + \lambda (X_{kn} - X_{kj})a &\geq 0 \\
- \frac{1}{n} \sum_{i' > j} \mathsf{gap}_{i'} \mathbf{1}_{(i':n)}^\tran \hat{r} 
   + \lambda (X_{kn} - X_{kj})a &\geq 0 
\end{align*}
where $\mathsf{gap}_i = X_{ki} - X_{k,i-1}$. If $\frac{1}{2n} |\mathbf{1}_{(i:n)}^\tran \hat{r}| \leq \lambda a$ for all $i=1,...,n$, then we have that:

\begin{align*}
- \frac{1}{n} \sum_{i' > j} \mathsf{gap}_{i'} \mathbf{1}_{i':n}^\tran \hat{r}
   + \lambda (X_{kn} - X_{kj})a &\geq 0 \quad \Leftrightarrow \\
- \sum_{i' > j} \mathsf{gap}_{i'} \lambda a + \lambda (X_{kn} - X_{kj}) a &\geq 0\\
- (X_{kn} - X_{kj}) \lambda a + \lambda (X_{kn} - X_{kj}) a &\geq 0
\end{align*}

We have thus proven that there exist one solution $\{ \hat{d}_k \}_{k=1,...,p}$ such that $\hat{d}_k = 0$ for all $k \in S^c$. Furthermore, we have shown that the subgradient variables $\mathbf{u}_k$ of the solution $\{ \hat{d}_k \}$ can be chosen such that $\| \mathbf{u}_k \|_1 < 1$ for all $k \in S^c$.  We now prove that if $\{ \hat{d}'_k \}_{k = 1,..., p}$ is another solution, then it must be that $\hat{d}'_k = 0$ for all $k \in S^c$ as well.  \\

%% prove uniqueness of sparsity pattern.

We first claim that $\sum_{k=1}^p \bar{\Delta}_k \hat{d}_k = \sum_{k=1}^p \bar{\Delta}_k \hat{d}'_k$. If this were not true, then a convex combination of $\hat{d}_k, \hat{d}'_k$ would achieve a strictly lower objective on the quadratic term. More precisely, let $\zeta \in [0,1]$. If $\sum_{k=1}^p \bar{\Delta}_k \hat{d}'_k \neq \sum_{k=1}^p \bar{\Delta}_k \hat{d}_k$, then $\| Y - \sum_{k=1}^p \bar{\Delta}_k \big( \hat{d}_k + \zeta ( \hat{d}'_k - \hat{d}_k) \big) \|_2^2$ is strongly convex as a function of $\nu$. Thus, it cannot be that $\hat{d}_k$ and $\hat{d}'_k$ both achieve optimal objective and we have reached a contradiction.\\

Now, we look at the stationarity condition for both $\{ \hat{d}_k \}$ and $\{ \hat{d}'_k \}$. Let $\mathbf{u}_k \in \partial \| \bar{\Delta}_k \hat{d}_k \|_\infty$ and let $\mathbf{u}'_k \in \partial \| \bar{\Delta}_k \hat{d}'_k \|_\infty$ be the two sets of subgradients. Let $\{ \nu_{ki} \}_{k=1,..,p,\, i=1,...n-1}$ and $\{ \nu'_{ki} \}$ be the two sets of positivity dual variables. \footnote{since there is no positivity constraint on $d_{k1}$, we let $\nu_{k1} = 0$ always.}

@@

Since both solutions $(\hat{d}, \mathbf{u}, \nu)$ and $(\hat{d}', \mathbf{u}', \nu')$ must satisfy the stationarity condition, we have that:
\[
\bar{\Delta}^\tran ( Y - \bar{\Delta} \hat{d} ) 
   + \lambda \sum_{k=1}^p \bar{\Delta}_k^\tran \mathbf{u}_k - \nu = 
\bar{\Delta}^\tran ( Y - \bar{\Delta} \hat{d}' ) 
   + \lambda \sum_{k=1}^p \bar{\Delta}_k^\tran \mathbf{u}'_k - \nu' = 0
\] 
We multiply both sides of the above equation by $\hat{d}'$:
\[
\hat{d}'^{\tran}  \bar{\Delta}^\tran ( Y - \bar{\Delta} \hat{d} ) 
    + \lambda \sum_{k=1}^p \hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}_k - \hat{d}'^\tran \nu = \hat{d}'^{\tran}  \bar{\Delta}^\tran ( Y - \bar{\Delta} \hat{d}' ) 
    + \lambda \sum_{k=1}^p \hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}'_k - \hat{d}'^\tran \nu'
\]
Since $\bar{\Delta} \hat{d}_k = \bar{\Delta} \hat{d}$, $\hat{d}'^\tran \nu' = 0$ (complementary slackness), and $\hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}'_k  = \| \hat{f}'_k \|_\infty$ (where $\hat{f}'_k = \bar{\Delta}_k \hat{d}'_k$), we have that:
\[
\lambda \sum_{k=1}^p \hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}_k - \hat{d}'^\tran \nu = \lambda \sum_{k=1}^p \| \hat{f}'_k \|_\infty
\]
On one hand, $\hat{d}'$ is a feasible solution so $\hat{d}'^\tran \nu \geq 0$ and so 
\[
\sum_{k=1}^p \hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}_k \geq \sum_{k=1}^p \| \hat{f}'_k \|_\infty .
\]

On the other hand, by Holder's inequality:
\begin{align*}
\sum_{k=1}^p \hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}_k &\leq 
   \sum_{k=1}^p \| \hat{f}'_k \|_\infty \|\mathbf{u}_k \|_1 
\end{align*}

Since $\mathbf{u}_k$ can be chosen so that $\| \mathbf{u}_k \|_1 < 1$ for all $k \in S^c$, we would get a contradiction if $\| \hat{f}'_k \|_\infty > 0$ for some $k \in S^c$. We thus conclude that $\hat{d}'$ must follow the same sparsity pattern.\\

The second item in the theorem concerning optimization~\ref{opt:alternate_opt_concave} is proven in exactly the same way.

The Lagrangian of optimization~\ref{opt:alternate_opt_concave} is:
\[
\mathcal{L}_{\trm{cave}}(d_k, \nu_k) = 
  \frac{1}{2n} \big\| \hat{r} - \bar{\Delta}_k d_k \big \|_2^2 + 
  \lambda \| \bar{\Delta}_k d_k \|_\infty + \sum_{k=1}^p \sum_{i=2}^{n-1} \nu_{ki} d_{ki}
\]

The exact same reasoning applies to show that $\hat{d}_k = 0$ satisfies KKT conditions sufficient for optimality.

@@

Fix $j$ and $i$. $\hat{r}^\tran \mathbf{1}_{(i':n)_k}$ is then the sum of $n-i'+1$ random coordinates of $\hat{r}$. We will then use Serfling's theorem on the concentration of measure of sampling without replacement. (corollary~\ref{cor:serfling}) We must first bound $\| \hat{r} \|_\infty$ and $\frac{1}{n} \sum_{i=1}^n \hat{r}_i$ before we can use Serfling's results however.\\

@@

Let $\mathcal{C}^1$ denote the set of univariate convex functions supported on $[-b,b]$. Let $\mathcal{C}^1_B \equiv \{ f \in \mathcal{C}^1 \,:\, \| f \|_\infty \leq B \}$ denote the set of $B$-bounded univariate convex functions. \\

@@

By additive faithfulness of the AC/DC procedure, it is known that $f^*_k \neq 0$ or $g^*_k \neq 0$ for all $k \in S$. \\

@@

Suppose $f^*_k = 0$, then $g^*_k \neq 0$. When $n$ is large enough, $\hat{g}_k$ must not be zero or we would have another contradiction. \\

@@

We denote $\epsilon_{n,\delta} \equiv (sB) \sqrt{ \frac{sK^{**}(2sbB)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}$. Let $\mathcal{E}_{[\,]}$ denote the event that for each $h \in \mathcal{G}$, there exists $h_L$ in the $\epsilon$-bracketing such that $\|h-h_L\|_{L_{P_n}} \leq 2\epsilon + \epsilon_{n, \delta}$. $\mathcal{E}_{[\,]}$ has probability at most $1-\delta$ as shown.\\

@@

\begin{proof}
Let $\mathcal{G}$ denote the off-centered set of convex functions, that is, $\mathcal{G} \equiv \mathcal{C}^s - f_0$. Note that if $h \in \mathcal{G}$, then $\| h \|_\infty = \| f_0 - f \|_\infty \leq 4 s B$.\\

@@

%For a $h \in \mathcal{G}$, let $h_\epsilon$ denote a function in the $\epsilon$-bracketing of $\mathcal{G}$ closest to $h$. It obviously must be that $\| h - h_\epsilon \|_n \leq \| h - h_\epsilon \|_\infty \leq \epsilon$.\\

@@

\begin{lemma}
\label{lem:acdc_derivative_bound}
Let $f : [0,1]^p \rightarrow \R$ be a twice differentiable function. Suppose $p(\mathbf{x})$ is a density on $[0,1]^p$ such that $\partial_{x_k} p(\mathbf{x}_{-k} \given x_k)$ and $\partial_{x_k}^2 p(\mathbf{x}_{-k} \given x_k)$ are all continuous as functions of $x_k$. Let $\phi(\mathbf{x}_{-k})$ be a continuous function not dependent on $x_k$.\\

@@

\begin{proposition} (Proposition 16 in \cite{kim2014global})\\
\label{prop:convexbracket}
Let $\mathcal{C}$ be the set of convex functions supported on $[-b, b]^d$ and uniformly bounded by $B$. Then there exist constants $\epsilon_3$ and $K^{**}$, dependent on $d$, such that
\[
\log N_{[]} (2\epsilon, \mathcal{C}, L_2) \leq K^{**} \left( \frac{2bB}{\epsilon} \right)^{d/2}
\]
for all $\epsilon \in (0, B \epsilon_3]$.
\end{proposition}

@@

\begin{proof}
$|f_L(X_i) - f_U(X_i)|$ is at most $sB$. There are $N_{[]}(2\epsilon, \mathcal{C}^s, L_1(P))$ pairs $(f_L, f_U)$. The inequality follows from a direct application of union bound and Hoeffding Inequality.\\
\end{proof}

>>>>

We restate Theorem~\ref{thm:deterministic} first for convenience. 
The following holds regardless of whether we impose the Lipschitz condition in optimization~\ref{opt:alternate_opt} and optimization~\ref{opt:alternate_opt_concave}.

\begin{theorem} 
Let $\{\hat{d}_k \}_{k \in S}$ be a minimizer of the restricted regression, that is, the solution to optimization (\ref{opt:alternate_opt}) where we restrict $k \in S$. 
Let $\hat{r} \coloneqq Y - \sum_{k \in S} \bar{\Delta}_k \hat{d}_k$ be the restricted regression residual.

Suppose for all $k\in S^c$ and for all $i=1,...,n$, $\lambda_n > | \frac{1}{2n}
\hat{r}^\tran \mathbf{1}_{(i:n)}|$ where $\mathbf{1}_{(i:n)}$ is 1 on the coordinates of the $i$-th largest to the $n$-th largest entries of $X_k$ and 0 elsewhere.
Then the following are true:
\begin{enumerate}
\item Let $\hat{d}_k = 0$ for $k \in S^c$, then \{$\hat{d}_k\}_{k=1,...,p}$ is an optimal solution to optimization~\ref{opt:alternate_opt}. Furthermore, any solution to the optimization program \ref{opt:alternate_opt} must be zero on $S^c$.
\item For all $k \in S^c$, the solution to optimization~\ref{opt:alternate_opt_concave} must be zero and must be unique.
\end{enumerate}
\end{theorem}

\begin{proof} 
We will omit the Lipschitz constraint in our proof here. It can be
added in and easily verified that the result of the theorem still holds.

We begin by considering the first item in the conclusion of the theorem.
We will show that with $\{\hat{d}_k\}_{k=1,..,p}$ as constructed, we
can set the dual variables to satisfy the 
complementary slackness and stationary conditions: $\nabla_{d_k} \mathcal{L}(\hat{d})  = 0$ for all $k$.

@@

We now verify that stationarity holds also for $k \in S^c$. We fix one dimension $k \in S^c$ and let $\hat{r} = Y - \sum_{k' \in S} \bar{\Delta}_{k'} \hat{d}_{k'}$. 
The Lagrangian form of the optimization, in terms of just $d_k$, is
\[
\mathcal{L}(d_k, \nu_k) =
  \frac{1}{2n} \big\| Y - \sum_{k' \in S} \bar{\Delta}_{k'} d_{k'} 
  -  \bar{\Delta}_k d_k \big\|_2^2 
   + \lambda \| \bar{\Delta}_k d_k\|_\infty
  - \sum_{i=2}^{n-1} \nu_{ki} d_{ki}
\]
with the constraint that $v_i \geq 0$ for all $i$.

The derivative of the Lagrangian is
\begin{align*}
\partial_{d_k} \mathcal{L}(d_k) =  -\frac{1}{n} \bar{\Delta}_k^\tran ( Y - \sum_{k'\in S} \bar{\Delta}_{k'} d_{k'}  - \bar{\Delta}_k d_k )
        + \lambda \bar{\Delta}_k^\tran \mathbf{u}
      - \nu_k
\end{align*}
where $\mathbf{u}$ is the subgradient of $\| \bar{\Delta}_k d_k \|_\infty$, an $n$-vector such that $\| \mathbf{u}_T \|_1 = 1$ where $T = \{ i \,:\,  (\bar{\Delta}_k d_k)_i = \| \bar{\Delta}_k d_k \|_\infty \}$.

We now substitute in $d_{k'} = \hat{d}_{k'}$ for $k' \in S$, $d_k = 0$ for $k \in S$, and $r = \hat{r}$ and show that the duals can be set in a way to ensure that the derivatives are equal to zero,
\begin{align*}
\partial_{d_k} \mathcal{L}(\hat{d}_k) = -\frac{1}{n} \bar{\Delta}_k^\tran\hat{r} + \lambda \bar{\Delta}_k^\tran \mathbf{u}
           - \nu_k = 0 
\end{align*}
where $\| \mathbf{u} \| \leq 1$ and $\nu_k \geq 0$. It clear that to show stationarity, we only need to show that $-\frac{1}{n} \bar{\Delta}_k^\tran \hat{r} + \lambda \bar{\Delta}_k^\tran \mathbf{u} \geq 0$ where the inequality is element-wise.

Let us reorder the samples so that the $i$-th sample is the $i$-th smallest sample. 
We will construct $\gamma = 0$, and $\mathbf{u} = (-a, 0, ..., a)$ for
some $0 < a < 1/2$, where the coordinates of $\mathbf{u}$ correspond
to the new sample ordering. 
We then just need to show that
\begin{align*}
- \frac{1}{n} \bar{\Delta}_k^\tran \hat{r} + \lambda \bar{\Delta}_k^\tran \mathbf{u} &\geq 0 \quad \Leftrightarrow \\
- \frac{1}{n} \Delta_k^\tran \hat{r} + \lambda \Delta_k^\tran \mathbf{u} &\geq 0 \quad \Leftrightarrow\\
- \frac{1}{n} \sum_{i > j} (X_{ki} - X_{kj}) \hat{r}_i + \lambda (X_{kn} - X_{kj})a &\geq 0 \quad 
   \textrm{for each } j \\
- \frac{1}{n} \sum_{i > j} \sum_{j < i' \leq i} \mathsf{gap}_{i'} \hat{r}_i 
    + \lambda (X_{kn} - X_{kj})a &\geq 0 \\
- \frac{1}{n} \sum_{i' > j} \mathsf{gap}_{i'} \sum_{i \geq i'} \hat{r}_i 
    + \lambda (X_{kn} - X_{kj})a &\geq 0 \\
- \frac{1}{n} \sum_{i' > j} \mathsf{gap}_{i'} \mathbf{1}_{(i':n)}^\tran \hat{r} 
   + \lambda (X_{kn} - X_{kj})a &\geq 0 
\end{align*}
where $\mathsf{gap}_i = X_{ki} - X_{k,i-1}$. If $\frac{1}{2n} |\mathbf{1}_{(i:n)}^\tran \hat{r}| \leq \lambda a$ for all $i=1,...,n$, then we have that
\begin{align*}
- \frac{1}{n} \sum_{i' > j} \mathsf{gap}_{i'} \mathbf{1}_{i':n}^\tran \hat{r}
   + \lambda (X_{kn} - X_{kj})a &\geq 0 \quad \Leftrightarrow \\
- \sum_{i' > j} \mathsf{gap}_{i'} \lambda a + \lambda (X_{kn} - X_{kj}) a &\geq 0\\
- (X_{kn} - X_{kj}) \lambda a + \lambda (X_{kn} - X_{kj}) a &\geq 0.
\end{align*}
We have thus proven that there exists one solution $\{ \hat{d}_k
\}_{k=1,...,p}$ such that $\hat{d}_k = 0$ for all $k \in
S^c$. Furthermore, we have shown that the subgradient variables
$\mathbf{u}_k$ of the solution $\{ \hat{d}_k \}$ can be chosen such
that $\| \mathbf{u}_k \|_1 < 1$ for all $k \in S^c$.

We now prove that if $\{ \hat{d}'_k \}_{k = 1,..., p}$ is another
solution, then it must be that $\hat{d}'_k = 0$ for all $k \in S^c$ as
well.  We first claim that $\sum_{k=1}^p \bar{\Delta}_k \hat{d}_k =
\sum_{k=1}^p \bar{\Delta}_k \hat{d}'_k$. If this were not true, then a
convex combination of $\hat{d}_k, \hat{d}'_k$ would achieve a strictly
lower objective on the quadratic term. More precisely, let $\zeta \in
[0,1]$. If $\sum_{k=1}^p \bar{\Delta}_k \hat{d}'_k \neq \sum_{k=1}^p
\bar{\Delta}_k \hat{d}_k$, then $\| Y - \sum_{k=1}^p \bar{\Delta}_k
\big( \hat{d}_k + \zeta ( \hat{d}'_k - \hat{d}_k) \big) \|_2^2$ is
strongly convex as a function of $\nu$. Thus, it cannot be that
$\hat{d}_k$ and $\hat{d}'_k$ both achieve optimal objective, and we
have reached a contradiction.

Now, we look at the stationarity condition for both $\{ \hat{d}_k \}$
and $\{ \hat{d}'_k \}$. Let $\mathbf{u}_k \in \partial \|
\bar{\Delta}_k \hat{d}_k \|_\infty$ and let $\mathbf{u}'_k
\in \partial \| \bar{\Delta}_k \hat{d}'_k \|_\infty$ be the two sets
of subgradients. Let $\{ \nu_{ki} \}$ and $\{
\nu'_{ki} \}$ be the two sets of positivity dual
variables, for $k=1,..,p$ and $i=1,...n-1$.  Note that since there is no positivity constraint on
$d_{k1}$, we let $\nu_{k1} = 0$ always.

@@

Since both solutions $(\hat{d}, \mathbf{u}, \nu)$ and $(\hat{d}',
\mathbf{u}', \nu')$ must satisfy the stationarity condition, we have
that
\[
\bar{\Delta}^\tran ( Y - \bar{\Delta} \hat{d} ) 
   + \lambda \sum_{k=1}^p \bar{\Delta}_k^\tran \mathbf{u}_k - \nu = 
\bar{\Delta}^\tran ( Y - \bar{\Delta} \hat{d}' ) 
   + \lambda \sum_{k=1}^p \bar{\Delta}_k^\tran \mathbf{u}'_k - \nu' = 0.
\] 
Multiplying both sides of the above equation by $\hat{d}'$,
\[
\hat{d}'^{\tran}  \bar{\Delta}^\tran ( Y - \bar{\Delta} \hat{d} ) 
    + \lambda \sum_{k=1}^p \hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}_k - \hat{d}'^\tran \nu = \hat{d}'^{\tran}  \bar{\Delta}^\tran ( Y - \bar{\Delta} \hat{d}' ) 
    + \lambda \sum_{k=1}^p \hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}'_k - \hat{d}'^\tran \nu'.
\]
Since $\bar{\Delta} \hat{d}_k = \bar{\Delta} \hat{d}$, $\hat{d}'^\tran \nu' = 0$ (complementary slackness), and $\hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}'_k  = \| \hat{f}'_k \|_\infty$ (where $\hat{f}'_k = \bar{\Delta}_k \hat{d}'_k$), we have that
\[
\lambda \sum_{k=1}^p \hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}_k - \hat{d}'^\tran \nu = \lambda \sum_{k=1}^p \| \hat{f}'_k \|_\infty.
\]
On one hand, $\hat{d}'$ is a feasible solution so $\hat{d}'^\tran \nu \geq 0$ and so 
\[
\sum_{k=1}^p \hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}_k \geq \sum_{k=1}^p \| \hat{f}'_k \|_\infty .
\]
On the other hand, by H\"older's inequality,
\begin{align*}
\sum_{k=1}^p \hat{d}'^\tran_k \bar{\Delta}_k^\tran \mathbf{u}_k &\leq 
   \sum_{k=1}^p \| \hat{f}'_k \|_\infty \|\mathbf{u}_k \|_1 .
\end{align*}
Since $\mathbf{u}_k$ can be chosen so that $\| \mathbf{u}_k \|_1 < 1$ for all $k \in S^c$, we would get a contradiction if $\| \hat{f}'_k \|_\infty > 0$ for some $k \in S^c$. We thus conclude that $\hat{d}'$ must follow the same sparsity pattern.

The second item in the theorem concerning optimization~\ref{opt:alternate_opt_concave} is proven in exactly the same way. 
The Lagrangian of optimization~\ref{opt:alternate_opt_concave} is
\[
\mathcal{L}_{\trm{cave}}(d_k, \nu_k) = 
  \frac{1}{2n} \big\| \hat{r} - \bar{\Delta}_k d_k \big \|_2^2 + 
  \lambda \| \bar{\Delta}_k d_k \|_\infty + \sum_{k=1}^p \sum_{i=2}^{n-1} \nu_{ki} d_{ki}.
\]
The same reasoning applies to show that $\hat{d}_k = 0$ satisfies KKT conditions sufficient for optimality.
\end{proof}

@@

Fix $j$ and $i$. $\hat{r}^\tran \mathbf{1}_{(i':n)_k}$ is then the sum of $n-i'+1$ random coordinates of $\hat{r}$. We will then use Serfling's theorem on the concentration of measure of sampling without replacement. (corollary~\ref{cor:serfling}) We must first bound $\| \hat{r} \|_\infty$ and $\frac{1}{n} \sum_{i=1}^n \hat{r}_i$ before we can use Serfling's results however.

@@

Let $\mathcal{C}^1$ denote the set of univariate convex functions supported on $[-b,b]$. Let $\mathcal{C}^1_B \equiv \{ f \in \mathcal{C}^1 \,:\, \| f \|_\infty \leq B \}$ denote the set of $B$-bounded univariate convex functions.

@@

By additive faithfulness of the AC/DC procedure, it is known that $f^*_k \neq 0$ or $g^*_k \neq 0$ for all $k \in S$.

@@

Suppose $f^*_k = 0$, then $g^*_k \neq 0$. When $n$ is large enough, $\hat{g}_k$ must not be zero or we would have another contradiction.

@@

We denote $\epsilon_{n,\delta} \equiv (sB) \sqrt{ \frac{sK^{**}(2sbB)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}$. Let $\mathcal{E}_{[\,]}$ denote the event that for each $h \in \mathcal{G}$, there exists $h_L$ in the $\epsilon$-bracketing such that $\|h-h_L\|_{L_{P_n}} \leq 2\epsilon + \epsilon_{n, \delta}$. $\mathcal{E}_{[\,]}$ has probability at most $1-\delta$ as shown.

@@

\begin{proof}
Let $\mathcal{G}$ denote the off-centered set of convex functions, that is, $\mathcal{G} \equiv \mathcal{C}^s - f_0$. Note that if $h \in \mathcal{G}$, then $\| h \|_\infty = \| f_0 - f \|_\infty \leq 4 s B$.

@@

%For a $h \in \mathcal{G}$, let $h_\epsilon$ denote a function in the $\epsilon$-bracketing of $\mathcal{G}$ closest to $h$. It obviously must be that $\| h - h_\epsilon \|_n \leq \| h - h_\epsilon \|_\infty \leq \epsilon$.

@@

\begin{lemma}
\label{lem:acdc_derivative_bound}
Let $f : [0,1]^p \rightarrow \R$ be a twice differentiable function. Suppose $p(\mathbf{x})$ is a density on $[0,1]^p$ such that $\partial_{x_k} p(\mathbf{x}_{-k} \given x_k)$ and $\partial_{x_k}^2 p(\mathbf{x}_{-k} \given x_k)$ are all continuous as functions of $x_k$. Let $\phi(\mathbf{x}_{-k})$ be a continuous function not dependent on $x_k$.

@@

\begin{proposition} (Proposition 16 in \cite{kim2014global})
\label{prop:convexbracket}
Let $\mathcal{C}$ be the set of convex functions supported on $[-b, b]^d$ and uniformly bounded by $B$. Then there exist constants $\epsilon_3$ and $K^{**}$, dependent on $d$, such that
\[
\log N_{[]} (2\epsilon, \mathcal{C}, L_2) \leq K^{**} \left( \frac{2bB}{\epsilon} \right)^{d/2}
\]
for all $\epsilon \in (0, B \epsilon_3]$.
\end{proposition}

@@

\begin{proof}
$|f_L(X_i) - f_U(X_i)|$ is at most $sB$. There are $N_{[]}(2\epsilon, \mathcal{C}^s, L_1(P))$ pairs $(f_L, f_U)$. The inequality follows from a direct application of union bound and Hoeffding Inequality.
\end{proof}
